Tables

### 2022-05-26 analysis/tables.Rmd
fix: column index in zlog colored table

```{r tables_raw_zlog, results = "asis", echo = FALSE, message = FALSE}
k <- kableExtra::kable_classic(
    kableExtra::kbl(
        imp_data,
        digits = 2,
        escape = FALSE
    ),
    "basic"
)
for (i in grep("_[CEQS]$", colnames(imp_data)))
    k <- kableExtra::column_spec(
            k, i,
            background = zcol(zlog_data[[i]]),
            popover = paste0("zlog: ", round(zlog_data[[i]], 2))
    )
k |> kableExtra::scroll_box(width = "100%", height = "500px")
```

>>>>

```{r tables_raw_zlog, results = "asis", echo = FALSE, message = FALSE}
k <- kableExtra::kable_classic(
    kableExtra::kbl(
        imp_data,
        digits = 2,
        escape = FALSE
    ),
    "basic"
)
for (i in grep("_[CEQS]$", colnames(imp_data)))
    k <- kableExtra::column_spec(
            k, i + 1,
            background = zcol(zlog_data[[i]]),
            popover = paste0("zlog: ", round(zlog_data[[i]], 2))
    )
k |> kableExtra::scroll_box(width = "100%", height = "500px")
```
